Statistical analysis of periodic data in neuroscience

### 2021-01-02 manuscript/manuscript.Rmd
Added new figure

nsims <- 100  # global value for the whole script - increase to 100000 for final run, but note this takes around 15 hours to complete

@@

@@

A convenient way to analyse the data from periodic stimulation experiments is to take the Fourier transform of the measured signal. The amplitude of the response at the stimulation frequency (and its harmonics - integer multiples of the stimulation frequency) is a precise and well-isolated index of the brain's response. Fourier spectra comprise both amplitude and phase information, which can be equivalently expressed as complex numbers with real and imaginary components. In many studies the phase information is routinely discarded, and statistical comparisons are performed on the amplitude data only. However an alternative is to use multivariate statistics, which take into account both the amplitude and phase information (represented as real and imaginary components). Multivariate methods have the advantage that they are more sensitive to weak signals, and therefore offer increased statistical power relative to univariate methods.

@@

text(0.5,19,'x',adj=0.5,cex=1.5)
text(4,13.5,'y',adj=0.5,cex=1.5)

@@

# lines(seq(0,10,0.01)+(d-1)*12,10*pnorm(seq(-5,5,0.01)),lwd=2)
# q <- quantile(scale(absvals),probs=seq(0,1,0.001))
# lines(5+q+(d-1)*12,seq(0,10,0.01),lwd=2,col=nbdtpal[d])

@@

par(pty="s")
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(1,5), ylim=c(0,4))
ticklocsx <- seq(1,5,1)    # locations of tick marks on x axis
ticklocsy <- seq(0,4,1)    # locations of tick marks on y axis
ticklabelsx <- 2^ticklocsx        # set labels for x ticks
ticklabelsy <- seq(0,4,1)    # set labels for y ticks
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)  
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Number of observations", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Effect size (d)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(expression(T^2),cex.main=2)
image(slist,dlist,tsqpropM,zlim=c(0,1),add=TRUE,col=kovesi.linear_blue_95_50_c20(256))
text(1.1,3.8,'(d)',cex=2)
legend(3.4,3.8,c('0','0.5','1'),lwd=6,cex=1.5,col=kovesi.linear_blue_95_50_c20(3),box.lwd=2,bg='white',title='Proportion')

@@

```{r powerfig2, fig.cap="Simulations comparing the sensitivity of MANOVA and ANOVA2circ. The format mirrors that of Figure 2. In these simulations, there were three conditions, with the signal being added to one condition only.", fig.align="center", echo=FALSE, fig.width=12, fig.height=8}

@@

par(pty="s")
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(1,5), ylim=c(0,4))
ticklocsx <- seq(1,5,1)    # locations of tick marks on x axis
ticklocsy <- seq(0,4,1)    # locations of tick marks on y axis
ticklabelsx <- 2^ticklocsx        # set labels for x ticks
ticklabelsy <- seq(0,4,1)    # set labels for y ticks
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)  
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Number of observations", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Effect size (d)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(expression('MANOVA'),cex.main=2)
image(slist,dlist,manovapropM,zlim=c(0,1),add=TRUE,col=kovesi.linear_blue_95_50_c20(256))
text(1.1,3.8,'(d)',cex=2)
legend(3.4,3.8,c('0','0.5','1'),lwd=6,cex=1.5,col=kovesi.linear_blue_95_50_c20(3),box.lwd=2,bg='white',title='Proportion')

>>>>

nsims <- 100  # global value for the whole script - increase to 100000 for final run, but note this takes around 16 hours to complete (depending on processor speed)

@@

getbanana <- function(p){
  thetaRange <- seq(0.01, pi, 0.01)
  Tval <- atan((p[3]*tan(thetaRange))/p[4])
  x1 <- p[1] + (p[3] * cos(Tval))
  x2 <- p[1] - (p[3] * cos(Tval))
  y <- p[2] + (p[4] * sin(Tval))

  XXX <- c(x1[1:(length(x1)/2)], x2[(length(x2)/2):1])
  Y <- c(y[1:(length(y)/2)], y[(length(y)/2):1], y[length(y):(1+length(y)/2)], y[(1+length(y)/2):length(y)])
  X <- c(XXX, XXX[length(XXX):1])
  errormatrix <- pol2cart(matrix(data=c(Y,X),ncol=2))
  return(errormatrix)
}

@@

A convenient way to analyse the data from periodic stimulation experiments is to take the Fourier transform of the measured signal. The amplitude of the response at the stimulation frequency (and its harmonics - integer multiples of the stimulation frequency) is a precise and well-defined index of the brain's response (see Figure \@ref(fig:fourierexplain)a,b). Fourier spectra comprise both amplitude and phase information that can be expressed in polar coordinates (Figure \@ref(fig:fourierexplain)c), or equivalently as complex numbers with real and imaginary components (Figure \@ref(fig:fourierexplain)d). In many studies the phase information is routinely discarded, and statistical comparisons are performed on the amplitude data only. However an alternative is to use multivariate statistics, which take into account both the amplitude and phase information (represented as real and imaginary components). Multivariate methods have the advantage that they are more sensitive to weak signals, and therefore offer increased statistical power relative to univariate methods.

```{r fourierexplain, fig.cap="Illustration of the principles of Fourier analysis for time-varying signals. Panel (a) shows a sinusoidal signal waveform, and simulated neural responses for successive observations (repetitions in the same individual, or recorded from multiple individuals). Panel (b) shows the Fourier amplitude spectra of the waveforms in (a), with clear peaks at the signal frequency (5Hz) in each example. The Fourier spectrum also includes a phase term, which can be represented in polar coordinates (amplitude and phase); panel (c) shows this for example responses at the signal frequency (grey points) and their average (blue point), which is computed separately for amplitude and phase terms. Alternatively, the same information is contained in a Cartesian representation of the real and imaginary parts of the complex spectrum (panel (d)). Notice that the individual observations (grey points) are the same in panels (c,d), but the different representations have implications for how the average (blue points) and measures of spread (shaded regions) are calculated.", fig.align="center", echo=FALSE, fig.width=9, fig.height=8}

set.seed(170382)

plotlims <- c(0,2.4,0,6) 
ticklocsx <- seq(0,1,0.5)    # locations of tick marks on x axis
ticklocsy <- seq(0,0.1,0.02)    # locations of tick marks on y axis
ticklabelsx <- ticklocsx        # set labels for x ticks
ticklabelsy <- ticklocsy    # set labels for y ticks

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
axis(1, at=seq(0,1,0.2), tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(1, at=seq(1.4,2.4,0.1), tck=0.01, lab=F, lwd=2) 
mtext(text = seq(0,1,0.2), side = 1, at=seq(0,1,0.2), line=0.2)
mtext(text = seq(0,20,2), side = 1, at=seq(1.4,2.4,0.1), line=0.2)
mtext(text = 'Time (s)', side = 1, cex=1.5, line=1.7, at=0.5) 
mtext(text = 'Frequency (Hz)', side = 1, cex=1.5, line=1.7, at=1.9)

text(1.2,5.5,'Signal',cex=1.2,adj=0.5)
text(1.2,4.5,'Observation',cex=1,adj=0.5)
text(1.2,3.75,'1',cex=1.2,adj=0.5)
text(1.2,2.75,'2',cex=1.2,adj=0.5)
text(1.2,1.75,'3',cex=1.2,adj=0.5)
text(1.2,1.1,'.',cex=1.2,adj=0.5)
text(1.2,1,'.',cex=1.2,adj=0.5)
text(1.2,0.9,'.',cex=1.2,adj=0.5)
text(1.2,0.25,'N',cex=1.2,adj=0.5)

text(0,5.8,'(a)',cex=1.5,adj=0.5)
text(1.45,5.8,'(b)',cex=1.5,adj=0.5)

tvals <- seq(0,10-0.001,0.001)
fvals <- c(0:(length(tvals)/2-1),(length(tvals)/2-1):0)/10
signal <- 0.8*cos(5*tvals * 2*pi + pi)

lines(tvals[1:1000],5+(signal[1:1000]+1)/2,lwd=2)

fsignal <- abs(fft(signal))/length(signal)
lines(1.4+fvals[10:200]/20,5+(2*fsignal[10:200]),lwd=2)

signal <- 0.8*cos(5*tvals * 2*pi + 3*pi/2)
ypos <- c(0,1.5,2.5,3.5)
for (n in 1:4){
nspec <- ((fft(signal)/length(signal)) + 0.2*rnorm(length(fvals))/fvals)
nspec[c(1:10,9991:10000)] <- 0
lines(1.4+fvals[10:200]/20,ypos[n]+(2*abs(nspec[10:200])),lwd=2)

nsignal <- Re(fft(nspec, inverse=TRUE))
nsignal <- nsignal[1:1000]/max(abs(nsignal[1:1000]))
nsignal <- nsignal - mean(nsignal)
lines(tvals[1:1000],ypos[n]-0.5+(nsignal[1:1000]+1),lwd=2)
}

signal <- 0.4*cos(5*tvals * 2*pi + pi/4)
allsimsignals <- NULL
nspec <- fft(signal)/length(signal)
for (n in 1:20){
  respec <- Re(nspec) + 1*rnorm(length(fvals))/fvals
  imspec <- Im(nspec) + 1*rnorm(length(fvals))/fvals

  allsimsignals[n] <- complex(real=respec[51],imaginary=imspec[51])
}

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-1,3.8), ylim=c(-1,1))

rangles <- seq(0,360)*(pi/180)
r <- seq(0.2,1,0.2)
for (n in 1:length(r)){
  lines(r[n]*cos(rangles),r[n]*sin(rangles),col='gray')
}
lines(c(0,0),c(-1,1),lwd=2)
lines(cos(c(30,210)*pi/180),sin(c(30,210)*pi/180),lwd=2)
lines(cos(c(150,330)*pi/180),sin(c(150,330)*pi/180),lwd=2)

text(0.5,-0.2,'Amplitude',cex=1.2,adj=0.5,srt=-30)
text(1.1,0,'Phase',cex=1.2,adj=0.5,srt=-90)

stdresps <- sd(Mod(allsimsignals))
stdangles <- sd(Arg(allsimsignals))
pvals <- getbanana(c(mean(Mod(allsimsignals)),Arg(mean(allsimsignals)),stdresps,stdangles))
polygon(pvals[,1], pvals[,2], col=addalpha(nbdtpal[3],0.2), border=NA)

for (n in 1:length(allsimsignals)){lines(c(0,Re(allsimsignals[n])),c(0,Im(allsimsignals[n])),col=addalpha(nbdtpal[1],0.5))}
points(Re(allsimsignals),Im(allsimsignals),pch=16,col=addalpha(nbdtpal[1],0.5),cex=0.8)

meanangle <- mean(((Arg(allsimsignals)-1) %% 2*pi)+1)
meanangle <- Arg(mean(allsimsignals))
meanamp <- mean(Mod(allsimsignals))
y <- meanamp*sin(meanangle)
x <- meanamp*cos(meanangle)
lines(c(0,x),c(0,y),lwd=3,col=nbdtpal[3])
points(x,y,pch=21,bg=nbdtpal[3],cex=1.5)

arrows(2.8,-1,2.8,1,length=0.1,lwd=2)
arrows(1.8,0,3.8,0,length=0.1,lwd=2)
text(1.93,0.1,'Real',cex=1.2,adj=0.5)
text(2.7,-0.7,'Imaginary',cex=1.2,adj=0.5,srt=90)

points(Re(allsimsignals)+2.8,Im(allsimsignals),pch=16,col=addalpha(nbdtpal[1],0.5),cex=0.8)
points(Re(mean(allsimsignals))+2.8,Im(mean(allsimsignals)),pch=21,bg=nbdtpal[3],cex=1.5)
eldata <- getel(allsimsignals)
polygon(eldata[1,]+2.8,eldata[2,], col=addalpha(nbdtpal[3],0.2), border=NA)

text(-1,1,'(c)',cex=1.5,adj=0.5)
text(1.8,1,'(d)',cex=1.5,adj=0.5)

@@

text(0.6,19,'Re',adj=0.5,cex=1.5)
text(4,13.6,'Im',adj=0.5,cex=1.5,srt=90)

@@

@@

par(pty="s")
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(1,5), ylim=c(0,4))
ticklocsx <- seq(1,5,1)    # locations of tick marks on x axis
ticklocsy <- seq(0,4,1)    # locations of tick marks on y axis
ticklabelsx <- 2^ticklocsx        # set labels for x ticks
ticklabelsy <- seq(0,4,1)    # set labels for y ticks
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)  
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Number of observations", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Effect size (d)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(expression(T^2),cex.main=2)
image(slist,dlist,tsqpropM,zlim=c(0,1),add=TRUE,col=kovesi.linear_blue_95_50_c20(256))
text(1.1,3.8,'(d)',cex=2)
legend(3.4,3.8,c('0','0.5','1'),lwd=6,cex=1.5,col=kovesi.linear_blue_95_50_c20(3),box.lwd=2,bg='white',title='Power')

@@

```{r powerfig2, fig.cap="Simulations comparing the sensitivity of MANOVA and ANOVA2circ. The format mirrors that of Figure 3. In these simulations, there were three conditions, with the signal being added to one condition only.", fig.align="center", echo=FALSE, fig.width=12, fig.height=8}

@@

par(pty="s")
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(1,5), ylim=c(0,4))
ticklocsx <- seq(1,5,1)    # locations of tick marks on x axis
ticklocsy <- seq(0,4,1)    # locations of tick marks on y axis
ticklabelsx <- 2^ticklocsx        # set labels for x ticks
ticklabelsy <- seq(0,4,1)    # set labels for y ticks
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)  
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.2)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
title(xlab="Number of observations", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
title(ylab="Effect size (d)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(expression('MANOVA'),cex.main=2)
image(slist,dlist,manovapropM,zlim=c(0,1),add=TRUE,col=kovesi.linear_blue_95_50_c20(256))
text(1.1,3.8,'(d)',cex=2)
legend(3.4,3.8,c('0','0.5','1'),lwd=6,cex=1.5,col=kovesi.linear_blue_95_50_c20(3),box.lwd=2,bg='white',title='Power')

### 2021-01-02 manuscript/manuscript.tex
Added new figure

\title{Statistical analysis of periodic data in neuroscience}
\author{Daniel H. Baker}
\date{2021-01-01}

@@

A convenient way to analyse the data from periodic stimulation experiments is to take the Fourier transform of the measured signal. The amplitude of the response at the stimulation frequency (and its harmonics - integer multiples of the stimulation frequency) is a precise and well-isolated index of the brain's response. Fourier spectra comprise both amplitude and phase information, which can be equivalently expressed as complex numbers with real and imaginary components. In many studies the phase information is routinely discarded, and statistical comparisons are performed on the amplitude data only. However an alternative is to use multivariate statistics, which take into account both the amplitude and phase information (represented as real and imaginary components). Multivariate methods have the advantage that they are more sensitive to weak signals, and therefore offer increased statistical power relative to univariate methods.

@@

\caption{Simulations comparing the sensitivity of MANOVA and ANOVA2circ. The format mirrors that of Figure 2. In these simulations, there were three conditions, with the signal being added to one condition only.}\label{fig:powerfig2}
\end{figure}

@@

The flowchart in Figure \ref{fig:flowchart} contains a proposed decision structure for the analysis of periodic data, once any outliers have been removed. Initially, data for each condition should be tested against the expected distribution of eigenvalue ratios using the condition index test. Comparisons with one or two conditions should be tested with the \(T^2_{circ}\) statistic if the eigenvalue ratios are consistent with circularity, and the \(T^2\) statistic if not. Comparisons with more than two conditions should be tested with the \(ANOVA^2_{circ}\) statistic if the eigenvalue ratios are consistent with circularity, or a MANOVA if not. Many MANOVA implementations cannot deal correctly with random factors (repeated measures) in complex factorial designs. However the \emph{multRM} function in the {[}\emph{MANOVA.RM}{]}\{\url{https://CRAN.R-project.org/package=MANOVA.RM}\} package (Friedrich et al., 2019) is able to handle such designs appropriately using a bootstrapping approach.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Afsari2014}{}%
Afsari F, Christensen KV, Smith GP, Hentzer M, Nippe OM, Elliott CJH, Wade AR. 2014. Abnormal visual gain control in a parkinson's disease model. \emph{Hum Mol Genet} \textbf{23}:4465--78. doi:\href{https://doi.org/10.1093/hmg/ddu159}{10.1093/hmg/ddu159}

@@

\leavevmode\hypertarget{ref-Engel1994}{}%
Engel SA, Rumelhart DE, Wandell BA, Lee AT, Glover GH, Chichilnisky EJ, Shadlen MN. 1994. FMRI of human visual cortex. \emph{Nature} \textbf{369}:525. doi:\href{https://doi.org/10.1038/369525a0}{10.1038/369525a0}

@@

\leavevmode\hypertarget{ref-Hotelling1931}{}%
Hotelling H. 1931. The generalization of student's ratio. \emph{The Annals of Mathematical Statistics} \textbf{2}:360--378.

@@

\leavevmode\hypertarget{ref-Hwang2020}{}%
Hwang E, Han H-B, Kim JY, Choi JH. 2020. High-density eeg of auditory steady-state responses during stimulation of basal forebrain parvalbumin neurons. \emph{Sci Data} \textbf{7}:288. doi:\href{https://doi.org/10.1038/s41597-020-00621-z}{10.1038/s41597-020-00621-z}

@@

\leavevmode\hypertarget{ref-Morrone1987}{}%
Morrone MC, Burr DC, Speed HD. 1987. Cross-orientation inhibition in cat is gaba mediated. \emph{Exp Brain Res} \textbf{67}:635--44. doi:\href{https://doi.org/10.1007/BF00247294}{10.1007/BF00247294}

@@

\leavevmode\hypertarget{ref-West2015}{}%
West RJH, Elliott CJH, Wade AR. 2015. Classification of parkinson's disease genotypes in drosophila using spatiotemporal profiling of vision. \emph{Sci Rep} \textbf{5}:16933. doi:\href{https://doi.org/10.1038/srep16933}{10.1038/srep16933}

>>>>

\title{Statistical analysis of periodic data in neuroscience}
\author{Daniel H. Baker}
\date{2021-01-02}

@@

A convenient way to analyse the data from periodic stimulation experiments is to take the Fourier transform of the measured signal. The amplitude of the response at the stimulation frequency (and its harmonics - integer multiples of the stimulation frequency) is a precise and well-defined index of the brain's response (see Figure \ref{fig:fourierexplain}a,b). Fourier spectra comprise both amplitude and phase information that can be expressed in polar coordinates (Figure \ref{fig:fourierexplain}c), or equivalently as complex numbers with real and imaginary components (Figure \ref{fig:fourierexplain}d). In many studies the phase information is routinely discarded, and statistical comparisons are performed on the amplitude data only. However an alternative is to use multivariate statistics, which take into account both the amplitude and phase information (represented as real and imaginary components). Multivariate methods have the advantage that they are more sensitive to weak signals, and therefore offer increased statistical power relative to univariate methods.

{\centering \includegraphics{manuscript_files/figure-latex/fourierexplain-1}

\caption{Illustration of the principles of Fourier analysis for time-varying signals. Panel (a) shows a sinusoidal signal waveform, and simulated neural responses for successive observations (repetitions in the same individual, or recorded from multiple individuals). Panel (b) shows the Fourier amplitude spectra of the waveforms in (a), with clear peaks at the signal frequency (5Hz) in each example. The Fourier spectrum also includes a phase term, which can be represented in polar coordinates (amplitude and phase); panel (c) shows this for example responses at the signal frequency (grey points) and their average (blue point), which is computed separately for amplitude and phase terms. Alternatively, the same information is contained in a Cartesian representation of the real and imaginary parts of the complex spectrum (panel (d)). Notice that the individual observations (grey points) are the same in panels (c,d), but the different representations have implications for how the average (blue points) and measures of spread (shaded regions) are calculated.}\label{fig:fourierexplain}
\end{figure}

@@

\caption{Simulations comparing the sensitivity of MANOVA and ANOVA2circ. The format mirrors that of Figure 3. In these simulations, there were three conditions, with the signal being added to one condition only.}\label{fig:powerfig2}
\end{figure}

@@

The flowchart in Figure \ref{fig:flowchart} contains a proposed decision structure for the analysis of periodic data, once any outliers have been removed. Initially, data for each condition should be tested against the expected distribution of eigenvalue ratios using the condition index test. Comparisons with one or two conditions should be tested with the \(T^2_{circ}\) statistic if the eigenvalue ratios are consistent with circularity, and the \(T^2\) statistic if not. Comparisons with more than two conditions should be tested with the \(ANOVA^2_{circ}\) statistic if the eigenvalue ratios are consistent with circularity, or a MANOVA if not. Many MANOVA implementations cannot deal correctly with random factors (repeated measures) in complex factorial designs. However the \emph{multRM} function in the \href{https://CRAN.R-project.org/package=MANOVA.RM}{\emph{MANOVA.RM}} package (Friedrich et al., 2019) is able to handle such designs appropriately using a bootstrapping approach.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Afsari2014}{}%
Afsari F, Christensen KV, Smith GP, Hentzer M, Nippe OM, Elliott CJH, Wade AR. 2014. Abnormal visual gain control in a Parkinson's disease model. \emph{Hum Mol Genet} \textbf{23}:4465--78. doi:\href{https://doi.org/10.1093/hmg/ddu159}{10.1093/hmg/ddu159}

@@

\leavevmode\hypertarget{ref-Engel1994}{}%
Engel SA, Rumelhart DE, Wandell BA, Lee AT, Glover GH, Chichilnisky EJ, Shadlen MN. 1994. fMRI of human visual cortex. \emph{Nature} \textbf{369}:525. doi:\href{https://doi.org/10.1038/369525a0}{10.1038/369525a0}

@@

\leavevmode\hypertarget{ref-Hotelling1931}{}%
Hotelling H. 1931. The generalization of Student's ratio. \emph{The Annals of Mathematical Statistics} \textbf{2}:360--378.

@@

\leavevmode\hypertarget{ref-Hwang2020}{}%
Hwang E, Han H-B, Kim JY, Choi JH. 2020. High-density EEG of auditory steady-state responses during stimulation of basal forebrain parvalbumin neurons. \emph{Sci Data} \textbf{7}:288. doi:\href{https://doi.org/10.1038/s41597-020-00621-z}{10.1038/s41597-020-00621-z}

@@

\leavevmode\hypertarget{ref-Morrone1987}{}%
Morrone MC, Burr DC, Speed HD. 1987. Cross-orientation inhibition in cat is GABA mediated. \emph{Exp Brain Res} \textbf{67}:635--44. doi:\href{https://doi.org/10.1007/BF00247294}{10.1007/BF00247294}

@@

\leavevmode\hypertarget{ref-West2015}{}%
West RJH, Elliott CJH, Wade AR. 2015. Classification of Parkinson's Disease Genotypes in Drosophila Using Spatiotemporal Profiling of Vision. \emph{Sci Rep} \textbf{5}:16933. doi:\href{https://doi.org/10.1038/srep16933}{10.1038/srep16933}
